Расчет фазового равновесия

### 2015-02-02 shevchenko/shevchenko/shevchenko.tex
Minor changes

%References
\selectlanguage{english}
\begin{thebibliography}{99}
\bibitem{Rozenberg_en} \textit{Rozenberg~M.D., Kundin~C.A.} Multiphase multicomponent filtration in oil and gas recovery. T. 1. --- M.: Nedra, 1976.
\bibitem{Chen_en} \textit{Chen~Z., Huan~G., Ma~Y.} Computational Methods for Multiphase Flows in Porous Media. --- Philadelphia: SIAM, 2006.
\bibitem{Batalin_en} \textit{Batalin~O.Y., Brusilovskiy~A.I., Zaharov~M.Y.} Phase equilibria in the systems of natural hydrocarbons. --- M.: Nedra, 1992.
\bibitem{Firoozabadi_en} \textit{Firoozabadi~A.} Thermodynamics of hydrocarbon reservoirs. --- New York: McGraw-Hill, 1999.
\bibitem{Orr_en} \textit{Orr~F.M.} Theory of gas injection processes. --- Copenhagen: Tie-Line Publications, 2007.
\bibitem{Prigozhin_en} \textit{Prigozhin~I., Defey~R.} Chemical thermodynamics. --- Novosibirsk: PH SB of RAS, 1966.
\bibitem{Sukharev_en} \textit{Sukharev~A.G.,Timokhov~A.V.,Fedorov~V.V.} The course of optimization methods. --- M.: FIZMATLIT, 2005.
\end{thebibliography}
\selectlanguage{russian}

>>>>

%References
\selectlanguage{english}
\begin{thebibliography}{99}
\bibitem{Rozenbergen} \textit{Rozenberg~M.D., Kundin~C.A.} Multiphase multicomponent filtration in oil and gas recovery. T. 1. --- M.: Nedra, 1976.
\bibitem{Chenen} \textit{Chen~Z., Huan~G., Ma~Y.} Computational Methods for Multiphase Flows in Porous Media. --- Philadelphia: SIAM, 2006.
\bibitem{Batalinen} \textit{Batalin~O.Y., Brusilovskiy~A.I., Zaharov~M.Y.} Phase equilibria in the systems of natural hydrocarbons. --- M.: Nedra, 1992.
\bibitem{Firoozabadien} \textit{Firoozabadi~A.} Thermodynamics of hydrocarbon reservoirs. --- New York: McGraw-Hill, 1999.
\bibitem{Orren} \textit{Orr~F.M.} Theory of gas injection processes. --- Copenhagen: Tie-Line Publications, 2007.
\bibitem{Prigozhinen} \textit{Prigozhin~I., Defey~R.} Chemical thermodynamics. --- Novosibirsk: PH SB of RAS, 1966.
\bibitem{Sukhareven} \textit{Sukharev~A.G.,Timokhov~A.V.,Fedorov~V.V.} The course of optimization methods. --- M.: FIZMATLIT, 2005.
\end{thebibliography}
\selectlanguage{russian}
